### 2023-03-12 main/chapter_2ljets.tex
explain why no light gmsb

For GMSB, only SR-$\llbb$ has sensitivity to large
$B(\neutralino_1 \to h \tilde{G})$ since it is able to capture the
resulting $h\to bb$ decays.
At its highest masses, the main SR-High regions retain sensitivity to its
$ZZ$ decays, and SR-High-1J again visibly extends the projected exclusion.
At its lowest masses, SR-Int and SR-Low both contribute.
These light GMSB signal models have substantial contaminations in VR-Low, which
are seen in Figure~\ref{fig:2ljets_low_region} to exceed $50\%$ of the central
background.
That SR-Int also provides sensitivity here is some comfort that this signal
contamination does not entirely invalidate the result.
We do not consider off-shell GMSB models, so SR-OffShell regions do not exclude
any points alone here.

@@

% TODO future expectations
% """
% • Sec 4.8 (Discussion): Expand on future expectations e.g. luminosities,
% heavier daughter particles with current data,
%
% HL-LHC and affect of pile-up,
% FCC etc.
% """

>>>>

For GMSB, only SR-$\llbb$ has sensitivity to large
$B(\neutralino_1 \to h \tilde{G})$ since it is able to capture the
resulting $h\to bb$ decays.
At its highest masses, the main SR-High regions retain sensitivity to its
$ZZ$ decays, and SR-High-1J again visibly extends the projected exclusion.
At its lowest masses, SR-Int and SR-Low both contribute.
These light GMSB signal models have substantial contaminations in VR-Low, which
are seen in Figure~\ref{fig:2ljets_low_region} to exceed $50\%$ of the central
background.
That SR-Int also provides sensitivity here is some comfort that this signal
contamination does not entirely invalidate the result.
We do not consider off-shell GMSB models because they are strongly excluded by
existing data%
\footnote{%
Each leg of our GMSB decay process has $\neutralino_1\to h/Z\gravitino$ with a
light $\gravitino$; $m(\gravitino) = 1$.
An off-shell decay therefore requires
$m(\neutralino_1) < m(Z) + 1\,\eV[G] \approx 92.2\,\eV[G]$.
This simplified GMSB model assumes $m(\neutralino_1) \approx m(\chargino_1)$,
and such a light $\chargino_1$ is excluded by LEP~2
searches~\cite{lepsusycombined}.
The CMS Collaboration has also published stronger constraints using proton
collision data from Run~1 of the LHC\cite{
cms_susy_2018_partial_run2_combination,
PhysRevD.90.092007
}.%
},
so SR-OffShell regions do not exclude any points alone here.

@@
